Syntax and Semantics of Abstract Binding Trees

### 2015-11-11 paper.tex
[paper] Improve layout of diagrams

By the Grothendieck construction
$\Iso{\Grothendieck{}{\Operators}}{\Comma{*}{\Operators}}$ we have a category
of elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are diagrams:
\[
  \begin{tikzcd}[ampersand replacement = \&]
    \& *
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
    \\
    {\Pair{\Upsilon}{a}}
      \arrow[rr, "\Pair{\rho}{f}", swap]
    \&
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]
We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\to\SCtx\times\Discrete{\Arities}}$
in which they reside:
\begin{alignat*}{3}
  &{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}&&\,\mathrel{\ {{:}}}\,&&\SCtx\times\Discrete{\Arities}\to\Sets\\
  &{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}&&\,=\,\ && %
    \{\ \ \Member{\vartheta}{\Pair{\Upsilon}{a}}\ \ |\ \
    {\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
    \Pair{\Upsilon}{a}\,\}
\end{alignat*}

@@

Then, $V$ is the unit to this tensor. We will say that an object
$\Of{P}{\widehat{\HypCat}^\Sorts}$ is a $\Sigma$-monoid in case it is equipped
with the following natural transformations where $\nu$ embeds variables into
$P$ and $\varsigma$ equips $P$ with an operation for simultaneous substitutions
of variables.

\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{V}} \arrow[r, "\IMode\nu"]
    \& {\IMode{P}}
    \& {\IMode{P\odot P}}
    \arrow[l, "\IMode\varsigma", swap]
  \end{tikzcd}
\]

%%TODO
We also have the induced maps $\Of{\nu_\Gamma}{V^{[\Gamma]}\to P^{[\Gamma]}}$
and
$\Of{\varsigma^\tau_{\Upsilon\parallel\Gamma}}{P_\tau^{\Yoneda{\Upsilon\parallel\Gamma}}
\times S^{\{\Upsilon\}}\times P^{[\Gamma]}\to P_\tau}$.

\begin{remark}
  A presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  also forms a \emph{relative monad}\footnote{Relative monads are skew-monoids
    in the skew-monoidal structure induced by a functor category
    $\mathbf{C}^\mathbf{J}$~\cite{altenkirch-chapman-uustalu:2015}. However,
    relative monads can also be understood without reference to monoids by
    viewing them as a generalization of \emph{extension systems} or
    \emph{Kleisli structures}. This latter presentation of monads, popular in
    computer science and logic, does not involve iteration of the monad
    functor.} on the functor $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
  Consequently, the monoid multiplication $\varsigma$ can be replaced with an
  extension operation:
  \[
    \begin{tikzcd}[ampersand replacement = \&, sep = huge]
      {\IMode{{P(\,=\,)}^{V(\,-\,)}}} \arrow[r, "{(\,-\,)}^{\circledast}"]
      \& {\IMode{{P(\,=\,)}^{P(\,-\,)}}}
    \end{tikzcd}
  \]
\end{remark}

@@

Then, the interpretation of a term in a model $P$ is a map from its environment
to $P$:
\[%
  \Of{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
      M:\tau}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P\to P_\tau}%
\]

The interpretation of a variable
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x:\tau}_P$ simply
projects it of the environment and embeds it into the model, as follows:
\[
  \begin{tikzcd}[ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_3}"]
    \& {\IMode{V^{[\Gamma]}}} \arrow[r, "\IMode{\nu_{\Gamma}}"]
    \& {\IMode{P^{[\Gamma]}}} \arrow[r, "\IMode{\pi_x}"]
    \& \IMode{P_\tau}
  \end{tikzcd}
  \tag{var}
\]

Next interpret metavariable applications
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash\MApp{\MV{m}}{\vec{u}}{\vec{M}}
: \tau}_P$ where
$\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}}$, which
proceeds by projecting the metavariable's interpretation from the environment
and intantiating it via substitution:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=7em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}"]
    \& {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
          \arrow[r, "\IMode{\varsigma^\tau_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \& \IMode{P_\tau}
  \end{tikzcd}
  \tag{metavar}
\]
where
\begin{gather*}
  \begin{tikzcd}[ampersand replacement = \&, sep=8em]
    {\IMode{S^{\{\Upsilon\}}}} \arrow[r, "\Define{\phi\,}{\,\Tuple{\pi_u}_{u\in\vec{u}}}"]
    \& {\IMode{S^{\{\vec{\sigma}\}}}}
  \end{tikzcd}\\
  \begin{tikzcd}[ampersand replacement = \&, sep=14em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
      \arrow[r, "\Define{\psi\,}{\,\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:\tau}_P}_{(M,\tau)\in (\vec{M},\vec{\tau})}}"]
    \& {\IMode{P^{[\vec{\tau}]}}}
  \end{tikzcd}
\end{gather*}

The interpretation of operator applications is most complicated. Recall that,
unlike in standard treatments of universal algebra, our operators are indexed
by symbol collections; therefore, operators must pass through suitable
renamings in order to be used in the interpretation. Let us begin by
constructing for each operator $\IsOperator{\Upsilon}{\vartheta}{a}$ the
morphism
$\Of{\SemBrackets{\vartheta}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
\to\Operators_{a}}$, which shall rename the parameters of the operator using
the environment. The natural transformation $\SemBrackets{\vartheta}_P$ is the
following composite:
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=large]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_2}"]
    \& {\IMode{S^{\{\Upsilon\}}}} \arrow[r, "\IMode{\FLift{\pi_{(-)}}{}}"]
    \& {\IMode{\Operators_a}}
  \end{tikzcd}
\]

We will proceed using the initial $\SigFun{\Sigma}$-algebra $\alpha$, as
follows, by postcomposing it with a morphism $\beta$ from the environment into
the signature endofunctor, which interprets the syntax of operator
applications:
\[
   \begin{tikzcd}[ampersand replacement = \&, sep=large]
     {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\beta}"]
     \& {\IMode{\SigFun{\Sigma}(P)_\tau}} \arrow[r, "\IMode{\alpha_\tau}"]
     \& {\IMode{P_\tau}}
   \end{tikzcd}
\]

The construction of $\beta$ proceeds by renaming the parameters of the operator
$\vartheta$ and constructing the (bound) arguments $\gamma$ of the operator.

\[
  \begin{tikzcd}[ampersand replacement = \&, sep=10em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
       \arrow[r, "\Define{\beta\,}{\,\Tuple{\SemBrackets{\vartheta}_P, \gamma}}"]
    \& {\IMode{%
       \coprod_{\vartheta\in \Operators_{\MkArity{\vec{v}}{\tau}}}%
       \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}%
       P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}%
    }}
  \end{tikzcd}
\]

Each argument
%
\begin{tikzcd}[ampersand replacement = \&]
  {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
    \arrow[r, "\IMode{\gamma_i}"]
  \& {\IMode{%
    P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}
  }}
\end{tikzcd}
%
is the exponential transpose of the composite,
\[
  \begin{tikzcd}[ampersand replacement = \&, sep=7.6em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\IMode{\Tuple{\pi_1\circ\pi_1,\phi_i,\psi_i}}"]
    \& {\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i}_P}}
      \arrow[r, "\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i\vdash M_i:\tau_i}_P}"]
    \& {\IMode{P_{\tau_i}}}
  \end{tikzcd}
\]
where $\phi_i,\psi_i$ are defined as follows:
\begin{gather*}
  \begin{tikzcd}[ampersand replacement = \&, sep=14em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\phi_i\,}{\,\Tuple{\pi_u\circ\pi_1}_{u\in\Dom{\Upsilon}},\, \Tuple{\pi_u\circ\pi_1\circ\pi_2}_{u\in\Dom{\vec{\sigma}_i}}}"]
    \& {\IMode{S^{\{\Upsilon,\vec{\sigma}_i\}}}}
  \end{tikzcd}\\
  \begin{tikzcd}[ampersand replacement = \&, sep=14em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\psi_i\,}{\,\Tuple{\pi_x\circ\pi_1}_{x\in\Dom{\Gamma}},\, \Tuple{\pi_x\circ\pi_1\circ\pi_2}_{x\in\Dom{\vec{\tau}_i}}}"]
    \& {\IMode{V^{[\Gamma,\vec{\tau}_i]}}}
  \end{tikzcd}
\end{gather*}

>>>>

By the Grothendieck construction
$\Iso{\Grothendieck{}{\Operators}}{\Comma{*}{\Operators}}$ we have a category
of elements of $\Operators$ where objects are triples
$\Pair{\Pair{\Upsilon}{a}}{\vartheta}$, interpreted as
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$, and morphisms are diagrams:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\Pair{\Upsilon}{a}}
      \arrow[r, "\Pair{\rho}{f}", swap]
    \& {\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, sep = small, ampersand replacement = \&]
    \& *
      \arrow[dl, "\vartheta", swap]
      \arrow[dr, "\vartheta'"]
    \&
    \\
    {\Operators\Pair{\Upsilon}{a}}
      \arrow[rr, "\Operators\Pair{\rho}{f}", swap]
    \&
    \& {\Operators\Pair{\Upsilon'}{a'}}
  \end{tikzcd}
\]
We will write $\IsOperator{\Upsilon}{\vartheta}{a}$ in case
$\Member{\vartheta}{\Operators\Pair{\Upsilon}{a}}$ and note that this judgment
enjoys the structural properties of weakening and exchange via functoriality of
$\Operators$. Operators $\vartheta_{0}, \ldots, \vartheta_{n}$ are defined by
specifying the fibers of
$\Of{\pi_{\Operators}}{\Grothendieck{}{\Operators}\to\SCtx\times\Discrete{\Arities}}$
in which they reside:
\begin{alignat*}{3}
  &{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}&&\,\mathrel{\ {{:}}}\,&&\SCtx\times\Discrete{\Arities}\to\Sets\\
  &{\pi_{\Operators}}^{-1}{\Pair{\Upsilon}{a}}&&\,=\,\ && %
    \{\ \ \Member{\vartheta}{\Pair{\Upsilon}{a}}\ \ |\ \
    {\pi_{\Operators}}{\Pair{\Pair{\Upsilon}{a}}{\vartheta}} =
    \Pair{\Upsilon}{a}\,\}
\end{alignat*}

@@

Then, $V$ is the unit to this tensor. We will say that an object
$\Of{P}{\widehat{\HypCat}^\Sorts}$ is a $\Sigma$-monoid in case it is equipped
with the following natural transformations where $\nu$ embeds variables into
$P$ and $\varsigma$ equips $P$ with an operation for simultaneous substitutions
of variables. Furthermore, $\nu$ and $\varsigma$ induce maps ${\nu}_{\Gamma}$ and
${{\varsigma}^{\tau}}_{\Upsilon\parallel\Gamma}$:
\vspace{-0.5em}
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{V}} \arrow[r, "\IMode\nu"]
    \& {\IMode{P}}
    \& {\IMode{P\odot P}}
    \arrow[l, "\IMode\varsigma", swap]
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{{V}^{[\Gamma]}}}
      \arrow[r, "\IMode{{\nu}_{\Gamma}}"]
    \& {\IMode{{P}^{[\Gamma]}}}
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, sep = large, ampersand replacement = \&]
    {\IMode{{P_\tau^{\Yoneda{\Upsilon\parallel\Gamma}}\times S^{\{\Upsilon\}}\times P^{[\Gamma]}}}}
      \arrow[r, "\IMode{\varsigma^\tau_{\Upsilon\parallel\Gamma}}"]
    \& {\IMode{P_\tau}}
  \end{tikzcd}
\]

\begin{remark}
  A presheaf $P$ with a substitution monoidal structure $\Pair{\nu}{\varsigma}$
  also forms a \emph{relative monad}\footnote{Relative monads are skew-monoids
    in the skew-monoidal structure induced by a functor category
    $\mathbf{C}^\mathbf{J}$~\cite{altenkirch-chapman-uustalu:2015}. However,
    relative monads can also be understood without reference to monoids by
    viewing them as a generalization of \emph{extension systems} or
    \emph{Kleisli structures}. This latter presentation of monads, popular in
    computer science and logic, does not involve iteration of the monad
    functor.} on the functor $\Of{V}{\widehat{\HypCat}^\Sorts}$ of variables.
  Consequently, the monoid multiplication $\varsigma$ can be replaced with an
  extension operation $\Of{{(\,-\,)}^{\circledast}}{{\IMode{{P(\,=\,)}^{V(\,-\,)}}}\to{\IMode{{P(\,=\,)}^{P(\,-\,)}}}}$.
\end{remark}

@@

Then, the interpretation of a term in a model $P$ is a map from its environment
to $P$:
\[%
  \Of{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash%
      M:\tau}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P\longrightarrow P_\tau}%
\]

The interpretation of a variable
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash x:\tau}_P$ simply
projects it of the environment and embeds it into the model, as follows:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_3}"]
    \& {\IMode{V^{[\Gamma]}}} \arrow[r, "\IMode{\nu_{\Gamma}}"]
    \& {\IMode{P^{[\Gamma]}}} \arrow[r, "\IMode{\pi_x}"]
    \& \IMode{P_\tau}
  \end{tikzcd}
  \tag{var}
\]

Next interpret metavariable applications
$\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash\MApp{\MV{m}}{\vec{u}}{\vec{M}}
: \tau}_P$ where
$\Lookup{\Omega}{\MV{m}}{\MkValence{\vec{\sigma}}{\vec{\tau}}{\tau}}$, which
proceeds by projecting the metavariable's interpretation from the environment
and intantiating it via substitution:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
          \arrow[r, "\IMode{\Tuple{\pi_\MV{m}\,\pi_1, \phi\,\pi_2, \psi}}"]
    \&[4.0em] {\IMode{P_{\tau}^{\Yoneda{\vec{\sigma}\parallel\vec{\tau}}}\times S^{\{\vec{\sigma}\}} \times P^{[\vec{\tau}]}}}
          \arrow[r, "\IMode{\varsigma^\tau_{\vec{\sigma}\parallel\vec{\tau}}}"]
    \&[1.0em] \IMode{P_\tau}
  \end{tikzcd}
  \tag{metavar}
\]
where
\vspace{-0.5em}
\begin{gather*}
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{S^{\{\Upsilon\}}}} \arrow[r, "\Define{\phi\,}{\,\Tuple{\pi_u}_{u\in\vec{u}}}"]
    \&[3.0em] {\IMode{S^{\{\vec{\sigma}\}}}}
  \end{tikzcd}
  \qquad\begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
      \arrow[r, "\Define{\psi\,}{\,\Tuple{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma\vdash M:\tau}_P}_{(M,\tau)\in (\vec{M},\vec{\tau})}}"]
    \&[11.0em] {\IMode{P^{[\vec{\tau}]}}}
  \end{tikzcd}
\end{gather*}

The interpretation of operator applications is most complicated. Recall that,
unlike in standard treatments of universal algebra, our operators are indexed
by symbol collections; therefore, operators must pass through suitable
renamings in order to be used in the interpretation. Let us begin by
constructing for each operator $\IsOperator{\Upsilon}{\vartheta}{a}$ the
morphism
$\Of{\SemBrackets{\vartheta}_P}{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
\to\Operators_{a}}$, which shall rename the parameters of the operator using
the environment. The natural transformation $\SemBrackets{\vartheta}_P$ is the
following composite:
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\pi_2}"]
    \& {\IMode{S^{\{\Upsilon\}}}} \arrow[r, "\IMode{\FLift{\pi_{(-)}}{}}"]
    \&[1.5em] {\IMode{\Operators_a}}
  \end{tikzcd}
\]

We will proceed using the initial $\SigFun{\Sigma}$-algebra $\alpha$, as
follows, by postcomposing it with a morphism $\beta$ from the environment into
the signature endofunctor, which interprets the syntax of operator
applications:
\[
   \begin{tikzcd}[cramped, ampersand replacement = \&]
     {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}} \arrow[r, "\IMode{\beta}"]
     \& {\IMode{\SigFun{\Sigma}(P)_\tau}} \arrow[r, "\IMode{\alpha_\tau}"]
     \& {\IMode{P_\tau}}
   \end{tikzcd}
\]

The construction of $\beta$ proceeds by renaming the parameters of the operator
$\vartheta$ and constructing the (bound) arguments $\gamma$ of the operator.
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
       \arrow[r, "\Define{\beta\,}{\,\Tuple{\SemBrackets{\vartheta}_P, \gamma}}"]
    \&[3.0em] {\IMode{%
       \coprod_{\vartheta\in \Operators_{\MkArity{\vec{v}}{\tau}}}%
       \prod_{\MkValence{\vec{\sigma}_i}{\vec{\tau}_i}{\tau_i}\in\vec{v}}%
       P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}%
    }}
  \end{tikzcd}
\]
Each argument
%
\begin{tikzcd}[cramped, ampersand replacement = \&]
  {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P}}
    \arrow[r, "\IMode{\gamma_i}"]
  \& {\IMode{%
    P_{\tau_i}^{\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}}
  }}
\end{tikzcd}
%
is the exponential transpose of the composite,
\[
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\IMode{\Tuple{\pi_1\circ\pi_1,\phi_i,\psi_i}}"]
    \&[4.0em] {\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i}_P}}
      \arrow[r, "\IMode{\SemBrackets{\Omega\triangleright\Upsilon,\vec{\sigma}_i\parallel\Gamma,\vec{\tau}_i\vdash M_i:\tau_i}_P}"]
    \&[7.5em] {\IMode{P_{\tau_i}}}
  \end{tikzcd}
\]
where $\phi_i,\psi_i$ are defined as follows:
\begin{gather*}
  \begin{tikzcd}[cramped, ampersand replacement = \&]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\phi_i\,}{\,\Tuple{\pi_u\circ\pi_1}_{u\in\Dom{\Upsilon}},\, \Tuple{\pi_u\circ\pi_1\circ\pi_2}_{u\in\Dom{\vec{\sigma}_i}}}"]
    \&[12.0em] {\IMode{S^{\{\Upsilon,\vec{\sigma}_i\}}}}\\[-1.0em]
    {\IMode{\SemBrackets{\Omega\triangleright\Upsilon\parallel\Gamma}_P
       \times\Yoneda{\vec{\sigma}_i\parallel\vec{\tau}_i}
    }}
      \arrow[r, "\Define{\psi_i\,}{\,\Tuple{\pi_x\circ\pi_1}_{x\in\Dom{\Gamma}},\, \Tuple{\pi_x\circ\pi_1\circ\pi_2}_{x\in\Dom{\vec{\tau}_i}}}"]
    \&[12.0em] {\IMode{V^{[\Gamma,\vec{\tau}_i]}}}
  \end{tikzcd}
\end{gather*}
